---
title: "R Notebook"
output:
  word_document: default
  html_notebook: default
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Load packages and libraries
```{r}
# install.packages("moments")
# install.packages("ggplot2")
# install.packages("corrplot")
# install.packages("tidyr")
# install.packages("dplyr")
# install.packages("ggridges")
# install.packages("mlbench")
# install.packages("lattice")
# install.packages("caret")
# install.packages("broom")
# install.packages("C50")
# install.packages("rpart")
# install.packages("pROC")
# install.packages("DMwR")
# install.packages("ROSE")
# install.packages('rattle')
# install.packages('rpart.plot')
# install.packages('RColorBrewer')
# install.packages("glmboost")
# install.packages("ROCR")
library(moments)
library(ggplot2)
library("corrplot")
library(tidyr)
library(dplyr)
library(ggridges)
library(mlbench)
library(caret)
library("C50")
library(rpart)
library(pROC)
library(DMwR)
library(ROSE)
library(rattle)
library(rpart.plot)
library(RColorBrewer)
library(ROCR)
```

# Load the dataset
```{r}
ccfraud <- read.csv("C:/Users/Kiran Kandhola/Documents/creditcardfraud/creditcard.csv",stringsAsFactors = FALSE)

```

# Reorder the levels of the "Class" attribute
```{r}
cc <- ccfraud                                       # Make a copy of the data
cc$Class <- as.factor(cc$Class)                     # Convert the class to factors
cc$Class <- factor(cc$Class, levels = c("1", "0"))  # Change the order of levels 
ccfd <- cc                    
levels(ccfd$Class) <- c("Fraud", "Genuine")         # Change the name of levels to Fraud and Genuine
```

## Stratified 80%- 20% splitting of the dataset into training and testing (time excluded)
```{r}
set.seed(7)
library(caret)
train_index <- createDataPartition(ccfd$Class,times = 1, p=0.8, list=FALSE)
ccfd <- ccfd[ ,-c(1)]
ccfd_train <- ccfd[train_index, ]
ccfd_test <- ccfd[-train_index, ]

zscorenormalize <- function(x){                               
                   return((x-mean(x))/(sd(x)))}

Amount_trn <- as.data.frame(lapply(ccfd_train[29], zscorenormalize))
ccfd_train <- as.data.frame(c(ccfd_train[1:28],Amount_trn,ccfd_train[30]))
Amount_tst <- as.data.frame(lapply(ccfd_test[29], zscorenormalize))
ccfd_test <- as.data.frame(c(ccfd_test[1:28],Amount_tst,ccfd_test[30]))

X_trn <- ccfd_train[ ,-30]
X_tst <- ccfd_test[ ,-30]

Y_trn <- ccfd_train[ ,30]
Y_tst <- ccfd_test[ ,30]

## stratified folds for cross-validation:
foldInd <- createFolds(Y_trn, k = 10, list = TRUE, returnTrain = TRUE)
lapply(foldInd, function(ii) table(Y_trn[ii]))
```

```{r}
set.seed(7)
library(caret)
train_index <- createDataPartition(cc$Class,times = 1, p=0.8, list=FALSE)

cc <- cc[ ,-c(1)]
cc_train <- cc[train_index, ]
cc_test <- cc[-train_index, ]

zscorenormalize <- function(x){                               
                   return((x-mean(x))/(sd(x)))}
Amount_train <- as.data.frame(lapply(cc_train[29], zscorenormalize))
cc_train <- as.data.frame(c(cc_train[1:28],Amount_train,cc_train[30]))
Amount_test <- as.data.frame(lapply(ccfd_test[29], zscorenormalize))
cc_test <- as.data.frame(c(ccfd_test[1:28],Amount_test,cc_test[30]))

X_train <- cc_train[ ,-30]
X_test <- cc_test[ ,-30]

Y_train <- cc_train[ ,30]
Y_test <- cc_test[ ,30]

## stratified folds for cross-validation:
foldInds <- createFolds(Y_train, k = 10, list = TRUE, returnTrain = TRUE)
lapply(foldInds, function(ii) table(Y_train[ii]))
```


# Training scheme for dataset using "smote" resampling
```{r}
ctr_s <- trainControl(index = foldInd,
                     method = "repeatedcv",
                     number = 10,
                     repeats = 3,
                     verboseIter = TRUE,
                     classProbs = TRUE,
                     sampling = "smote",
                     summaryFunction = twoClassSummary,
                     savePredictions = TRUE)
```

# rpart using "smote" resampling
```{r}
set.seed(10)
rpart_s <- train(Class ~., data = ccfd_train, method = "rpart", parms = list(split = "information"), metric = "ROC", trControl=ctr_s, tuneLength = 30)
```


```{r}
rpart_s

# test set results using confusion matrix
pred_rpart_s <- predict(rpart_s, ccfd_test)
confusionMatrix(pred_rpart_s, Y_tst)

# Predicting Class probabilities
prob_rpart_s <- predict(rpart_s, ccfd_test, type = "prob")
head(prob_rpart_s)

# AUC using pROC package
ROC_rpart_s <- roc(Y_tst, prob_rpart_s [ ,"Fraud"])
plot(ROC_rpart_s, print.thres = c(0.0001,0.001, 0.01, 0.1, 0.5, 0.999), col = "blue")
ROC_rpart_s

# AUC using ROCR package
pr_rpart_s <- prediction(prob_rpart_s[ , 1], Y_test)
prf_rpart_s <- performance(pr_rpart_s, measure = "tpr", x.measure = "fpr")
plot(prf_rpart_s, col = "blue")
abline(0,1)
auc_rs <- performance(pr_rpart_s, measure = "auc")
auc_rs <- auc_rs@y.values[[1]]
auc_rs
```

# C5.0 
```{r}
set.seed(10)
grid <- expand.grid(.model = "tree", 
                    .trials = c(1:10),
                    .winnow = FALSE)
C5_s <- train(X_trn, Y_trn, method = "C5.0", metric = "ROC", trControl=ctr_s, tuneGrid = grid)
```


```{r}
C5_s

# test set results using confusion matrix
pred_C5_s <- predict(C5_s, ccfd_test)
confusionMatrix(pred_C5_s, Y_tst)

# Predicting Class probabilities
prob_C5_s <- predict(C5_s, ccfd_test, type = "prob")
head(prob_C5_s)

#library(pROC)
ROC_C5_s <- roc(Y_tst, prob_C5_s [ ,"Fraud"])
plot(ROC_C5_s, print.thres = c(0.0001,0.001, 0.01, 0.1, 0.9, 0.999), col = "chocolate")
ROC_C5_s

# using ROCR package
pr_C5_s <- prediction(prob_C5_s[ , 1], Y_test)
prf_C5_s <- performance(pr_C5_s, measure = "tpr", x.measure = "fpr")
plot(prf_C5_s, col = "chocolate")
abline(0,1)
auc_C5s <- performance(pr_C5_s, measure = "auc")
auc_C5s <- auc_C5s@y.values[[1]]
auc_C5s

```

# Random forest
```{r}
set.seed(7)
rf_s <- train(Class ~ ., data = ccfd_train, method = "rf", trControl = ctr_s, verbose = F, metric = "ROC", tuneLength = 9)
rf_s
```


```{r}
pred_rf_s <- predict(rf_s, ccfd_test)
confusionMatrix(pred_rf_s, Y_tst)

# Predicting Class probabilities
prob_rf_s <- predict(rf_s, ccfd_test, type = "prob")
head(prob_rf_s)

#library(pROC)
ROC_rf_s <- roc(Y_tst, prob_rf_s [ ,"Fraud"])
plot(ROC_rf_s, print.thres = c(0.0001,0.001, 0.01, 0.1, 0.9, 0.999), col = "black")
ROC_rf_s

# using ROCR package
pr_rf_s <- prediction(prob_rf_s[ , 2], Y_tst)
prf_rf_s <- performance(pr_rf_s, measure = "tpr", x.measure = "fpr")
plot(prf_rf_s, col = "black")
abline(0,1)
auc_rf <- performance(pr_rf_s, measure = "auc")
auc_rf <- auc_rf@y.values[[1]]
auc_rf
```

# logistic Regression with smote resampling

```{r}
set.seed(777)
glm_s <- train(Class ~ ., data=ccfd_train, trControl=ctr_s, method="glm", family=binomial(), metric = "ROC")
summary(glm_s)
```


```{r}
summary(glm_s)
pred_glm_s <- predict(glm_s, ccfd_test)
confusionMatrix(pred_glm_s, Y_tst)

# Predicting Class probabilities
prob_glm_s <- predict(glm_s, ccfd_test, type = "prob")
head(prob_glm_s)

#library(pROC)
ROC_glm_s <- roc(Y_tst, prob_glm_s [ ,"Fraud"])
plot(ROC_glm_s, print.thres = c(0.0001,0.001, 0.01, 0.1,0.91, 0.999), col = "indianred2")
ROC_glm_s

# using ROCR package
pr_glm_s <- prediction(prob_glm_s[ , 1], Y_test)
prf_glm_s <- performance(pr_glm_s, measure = "tpr", x.measure = "fpr")
plot(prf_glm_s, col = "indianred2")
abline(0,1)
auc_glm <- performance(pr_glm_s, measure = "auc")
auc_glm <- auc_glm@y.values[[1]]
auc_glm
```


# k-nn with smote resampling
```{r}
gridk = expand.grid(k =c(5, 7, 9, 13, 17, 21, 27, 31, 37))
```

```{r}
set.seed(7)
knn_s <- train(X_trn, Y_trn, method = "knn", metric = "ROC", trControl=ctr_s, tuneGrid = gridk)
knn_s
```

```{r}
pred_knn_s <- predict(knn_s, ccfd_test)
confusionMatrix(pred_knn_s, Y_tst)

# Predicting Class probabilities
plot(knn_s)
prob_knn_s <- predict(knn_s, ccfd_test, type = "prob")
head(prob_knn_s)

#library(pROC)
ROC_knn_s <- roc(Y_tst, prob_knn_s [ ,"Fraud"])
plot(ROC_knn_s, print.thres = c(0.0001,0.001, 0.01, 0.1, 0.90, 0.999),col = "darkolivegreen1")
ROC_knn_s

# using ROCR package
pr_knn_s <- prediction(prob_knn_s[ , 1], Y_test)
prf_knn_s <- performance(pr_knn_s, measure = "tpr", x.measure = "fpr")
plot(prf_knn_s, col = "darkolivegreen1")
abline(0,1)
auc_knns <- performance(pr_knn_s, measure = "auc")
auc_knns <- auc_knns@y.values[[1]]
auc_knns
```


# SVM with smote resampling
```{r}
set.seed(10)
svm_s <- train(Class ~ ., data = ccfd_train, method = "svmRadial", trControl = ctr_s, metric = "ROC", tuneLength = 9)
svm_s
```

```{r}
pred_svm_s <- predict(svm_s, ccfd_test)
confusionMatrix(pred_svm_s, Y_tst)

# Predicting Class probabilities
prob_svm_s <- predict(svm_s, ccfd_test, type = "prob")
head(prob_svm_s)

#library(pROC)
ROC_svm_s <- roc(Y_tst, prob_svm_s [ ,"Fraud"])
plot(ROC_svm_s, print.thres = c(0.0001,0.001, 0.01, 0.1, 0.5, 0.9, 0.999), col = "orange")
ROC_svm_s

# using ROCR package
pr_svm_s <- prediction(prob_svm_s[ , 1], Y_test)
prf_svm_s <- performance(pr_svm_s, measure = "tpr", x.measure = "fpr")
plot(prf_svm_s, col = "orange")
abline(0,1)
auc_svm <- performance(pr_svm_s, measure = "auc")
auc_svm <- auc_svm@y.values[[1]]
auc_svm
```

```{r}
plot(prf_rpart_s,lty = 1,lwd = 2, col = "blue")
plot(prf_rf_s,lty = 1, lwd = 2, col = "black", add = TRUE)
plot(prf_glm_s,lty = 1, lwd = 2, col = "indianred2", add = TRUE)
plot(prf_knn_s,lty = 1, lwd = 2, col = "darkolivegreen1", add = TRUE)
plot(prf_svm_s,lty = 1, lwd = 2, col = "orange", add = TRUE)
legend ("topright", legend = c("rpart","rf", "glm", "knn", "svm"), col = c("blue", "black", "indianred2", "darkolivegreen1", "orange"), lwd = c(2,2,2,2,2,2))
```

