---
title: "R Notebook"
output:
  word_document: default
  html_notebook: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Load packages and libraries
```{r}
# install.packages("moments")
# install.packages("ggplot2")
# install.packages("corrplot")
# install.packages("tidyr")
# install.packages("dplyr")
# install.packages("ggridges")
# install.packages("mlbench")
# install.packages("lattice")
# install.packages("caret")
# install.packages("broom")
# install.packages("C50")
# install.packages("rpart")
# install.packages("pROC")
# install.packages("DMwR")
# install.packages("ROSE")
# install.packages('rattle')
# install.packages('rpart.plot')
# install.packages('RColorBrewer')
# install.packages("glmboost")
# install.packages("ROCR")
library(moments)
library(ggplot2)
library("corrplot")
library(tidyr)
library(dplyr)
library(ggridges)
library(mlbench)
library(caret)
library("C50")
library(rpart)
library(pROC)
library(DMwR)
library(ROSE)
library(rattle)
library(rpart.plot)
library(RColorBrewer)
library(ROCR)
```

# Load the dataset
```{r}
ccfraud <- read.csv("C:/Users/Kiran Kandhola/Documents/creditcardfraud/creditcard.csv",stringsAsFactors = FALSE)

```

# Reorder the levels of the "Class" attribute
```{r}
cc <- ccfraud                                       # Make a copy of the data
cc$Class <- as.factor(cc$Class)                     # Convert the class to factors
cc$Class <- factor(cc$Class, levels = c("1", "0"))  # Change the order of levels 
ccfd <- cc                    
levels(ccfd$Class) <- c("Fraud", "Genuine")         # Change the name of levels to Fraud and Genuine
```

## Stratified 80%- 20% splitting of the dataset into training and testing (time excluded)
```{r}
set.seed(7)
library(caret)
train_index <- createDataPartition(ccfd$Class,times = 1, p=0.8, list=FALSE)
ccfd <- ccfd[ ,-c(1)]
ccfd_train <- ccfd[train_index, ]
ccfd_test <- ccfd[-train_index, ]

zscorenormalize <- function(x){                               
                   return((x-mean(x))/(sd(x)))}

Amount_trn <- as.data.frame(lapply(ccfd_train[29], zscorenormalize))
ccfd_train <- as.data.frame(c(ccfd_train[1:28],Amount_trn,ccfd_train[30]))
Amount_tst <- as.data.frame(lapply(ccfd_test[29], zscorenormalize))
ccfd_test <- as.data.frame(c(ccfd_test[1:28],Amount_tst,ccfd_test[30]))

X_trn <- ccfd_train[ ,-30]
X_tst <- ccfd_test[ ,-30]

Y_trn <- ccfd_train[ ,30]
Y_tst <- ccfd_test[ ,30]

## stratified folds for cross-validation:
foldInd <- createFolds(Y_trn, k = 10, list = TRUE, returnTrain = TRUE)
lapply(foldInd, function(ii) table(Y_trn[ii]))
```

```{r}
set.seed(7)
library(caret)
train_index <- createDataPartition(cc$Class,times = 1, p=0.8, list=FALSE)

cc <- cc[ ,-c(1)]
cc_train <- cc[train_index, ]
cc_test <- cc[-train_index, ]

zscorenormalize <- function(x){                               
                   return((x-mean(x))/(sd(x)))}
Amount_train <- as.data.frame(lapply(cc_train[29], zscorenormalize))
cc_train <- as.data.frame(c(cc_train[1:28],Amount_train,cc_train[30]))
Amount_test <- as.data.frame(lapply(ccfd_test[29], zscorenormalize))
cc_test <- as.data.frame(c(ccfd_test[1:28],Amount_test,cc_test[30]))

X_train <- cc_train[ ,-30]
X_test <- cc_test[ ,-30]

Y_train <- cc_train[ ,30]
Y_test <- cc_test[ ,30]

## stratified folds for cross-validation:
foldInds <- createFolds(Y_train, k = 10, list = TRUE, returnTrain = TRUE)
lapply(foldInds, function(ii) table(Y_train[ii]))
```

# Training scheme for unbalanced dataset
```{r}
ctr_ub <- trainControl(index = foldInd,
                     method = "repeatedcv",
                     number = 10,
                     repeats = 3,
                     verboseIter = TRUE,
                     classProbs = TRUE,
                     summaryFunction = twoClassSummary,
                     savePredictions = TRUE)
```

# Training scheme for dataset using "smote" resampling
```{r}
ctr_s <- trainControl(index = foldInd,
                     method = "repeatedcv",
                     number = 10,
                     repeats = 3,
                     verboseIter = TRUE,
                     classProbs = TRUE,
                     sampling = "smote",
                     summaryFunction = twoClassSummary,
                     savePredictions = TRUE)
```

# Training scheme for dataset using "up" resampling
```{r}
ctr_up <- trainControl(index = foldInd,
                     method = "repeatedcv",
                     number = 10,
                     repeats = 3,
                     verboseIter = TRUE,
                     classProbs = TRUE,
                     sampling = "up",
                     summaryFunction = twoClassSummary,
                     savePredictions = TRUE)
```

# Training scheme for dataset using "down" resampling
```{r}
ctr_down <- trainControl(index = foldInd,
                     method = "repeatedcv",
                     number = 10,
                     repeats = 3,
                     verboseIter = TRUE,
                     classProbs = TRUE,
                     sampling = "down",
                     summaryFunction = twoClassSummary,
                     savePredictions = TRUE)
```

# Baseline model: Decision Tree

```{r}
set.seed(7)
fit_rpart <- rpart(Class ~ ., data = cc_train)
fit_rpartPred <- predict(fit_rpart, cc_test, type = "class")
confusionMatrix(fit_rpartPred,cc_test$Class)
```
```{r}
# Predicting Class probabilities
prob_fit_rpart <- predict(fit_rpart, cc_test, type = "prob")
head(prob_fit_rpart)

#library(pROC)
ROC_fit_rpart <- roc(Y_tst, prob_fit_rpart[ ,"1"])
plot(ROC_fit_rpart, print.thres = c(0.0001,0.001, 0.01, 0.1, 0.90, 0.999))
ROC_fit_rpart
```

# rpart on unbalanced full dataset
```{r}
set.seed(7)
rpart_ub <- train(Class ~., data = ccfd_train, method = "rpart", parms = list(split = "information"), metric = "ROC", trControl=ctr_ub, tuneLength = 30)
```

```{r}
rpart_ub

# test set results using confusion matrix
pred_rpart_ub <- predict(rpart_ub, ccfd_test)
confusionMatrix(pred_rpart_ub, Y_tst)

# Predicting Class probabilities
prob_rpart_ub <- predict(rpart_ub, ccfd_test, type = "prob")
head(prob_rpart_ub)

# AUC using pROC package
ROC_rpart_ub <- roc(Y_tst, prob_rpart_ub [ ,"Fraud"])
plot(ROC_rpart_ub, print.thres = c(0.0001,0.001, 0.01, 0.1, 0.90, 0.999), col = "violet")
ROC_rpart_ub

# AUC using ROCR package
pr_rpart_ub <- prediction(prob_rpart_ub[ , 1], Y_test)
prf_rpart_ub <- performance(pr_rpart_ub, measure = "tpr", x.measure = "fpr")
plot(prf_rpart_ub, col = "violet")
abline(0,1)
auc_rub <- performance(pr_rpart_ub, measure = "auc")
auc_rub <- auc_rub@y.values[[1]]
auc_rub
```

# rpart using "smote" resampling
```{r}
set.seed(10)
rpart_s <- train(Class ~., data = ccfd_train, method = "rpart", parms = list(split = "information"), metric = "ROC", trControl=ctr_s, tuneLength = 30)
```

```{r}
rpart_s

# test set results using confusion matrix
pred_rpart_s <- predict(rpart_s, ccfd_test)
confusionMatrix(pred_rpart_s, Y_tst)

# Predicting Class probabilities
prob_rpart_s <- predict(rpart_s, ccfd_test, type = "prob")
head(prob_rpart_s)

# AUC using pROC package
ROC_rpart_s <- roc(Y_tst, prob_rpart_s [ ,"Fraud"])
plot(ROC_rpart_s, print.thres = c(0.0001,0.001, 0.01, 0.1, 0.5, 0.999), col = "blue")
ROC_rpart_s

# AUC using ROCR package
pr_rpart_s <- prediction(prob_rpart_s[ , 1], Y_test)
prf_rpart_s <- performance(pr_rpart_s, measure = "tpr", x.measure = "fpr")
plot(prf_rpart_s, col = "blue")
abline(0,1)
auc_s <- performance(pr_rpart_s, measure = "auc")
auc_s <- auc_s@y.values[[1]]
auc_s
```


# rpart Using "up"" resampling
```{r}
set.seed(7)
rpart_up <- train(Class ~., data = ccfd_train, method = "rpart", parms = list(split = "information"), metric = "ROC", trControl=ctr_up, tuneLength = 30)
```

```{r}
rpart_up

# test set results using confusion matrix
pred_rpart_up <- predict(rpart_up, ccfd_test)
confusionMatrix(pred_rpart_up, Y_tst)

# Predicting Class probabilities
prob_rpart_up <- predict(rpart_up, ccfd_test, type = "prob")
head(prob_rpart_up)

# AUC using pROC package
ROC_rpart_up <- roc(Y_tst, prob_rpart_up [ ,"Fraud"])
plot(ROC_rpart_up, print.thres = c(0.0001,0.001, 0.01, 0.1, 0.5, 0.9, 0.999), col = "green")
ROC_rpart_up

# AUC using ROCR package
pr_rpart_up <- prediction(prob_rpart_up[ , 1], Y_test)
prf_rpart_up <- performance(pr_rpart_up, measure = "tpr", x.measure = "fpr")
plot(prf_rpart_up, col = "green")
abline(0,1)
auc_rup <- performance(pr_rpart_up, measure = "auc")
auc_rup <- auc_rup@y.values[[1]]
auc_rup

```


# rpart Using "down"" resampling
```{r}
set.seed(7)
rpart_down <- train(Class ~., data = ccfd_train, method = "rpart", parms = list(split = "information"), metric = "ROC", trControl=ctr_down, tuneLength = 30)
```

```{r}
rpart_down

# test set results using confusion matrix
pred_rpart_down <- predict(rpart_down, ccfd_test)
confusionMatrix(pred_rpart_down, Y_tst)

# Predicting Class probabilities
prob_rpart_down <- predict(rpart_down, ccfd_test, type = "prob")
head(prob_rpart_down)

# AUC using pROC package
ROC_rpart_down <- roc(Y_tst, prob_rpart_down [ ,"Fraud"])
plot(ROC_rpart_down, print.thres = c(0.0001,0.001, 0.01, 0.1, 0.5, 0.9, 0.999), col = "lightblue")
ROC_rpart_down

# AUC using ROCR package
pr_rpart_down <- prediction(prob_rpart_down[ , 1], Y_test)
prf_rpart_down <- performance(pr_rpart_down, measure = "tpr", x.measure = "fpr")
plot(prf_rpart_down, col = "lightblue")
abline(0,1)
auc_rd <- performance(pr_rpart_down, measure = "auc")
auc_rd <- auc_rd@y.values[[1]]
auc_rd
```

# Stratified 80% - 20% splitting of the dataset into training and testing (V4, V8, V10, V12, V14, V16, V17, V21, V27, and Amount)
```{r}
set.seed(7)
train_id <- createDataPartition(ccfd$Class,times = 1, p=0.8, list=FALSE)

ccf <- ccfd[ , c("V4", "V8", "V10", "V12", "V14", "V16", "V17", "V21", "V27", "Amount", "Class")]
ccf_train <- ccf[train_id, ]
ccf_test <- ccf[-train_id, ]

zscorenormalize <- function(x){                               
                   return((x-mean(x))/(sd(x)))}

Amount_tr <- as.data.frame(lapply(ccf_train[10], zscorenormalize))
ccf_train <- as.data.frame(c(ccf_train[1:9],Amount_tr,ccf_train[11]))
Amount_ts <- as.data.frame(lapply(ccf_test[10], zscorenormalize))
ccf_test <- as.data.frame(c(ccf_test[1:9],Amount_ts,ccf_test[11]))

X_tr <- ccf_train[ ,-11]
X_ts <- ccf_test[ ,-11]

Y_tr <- ccf_train[ ,11]
Y_ts <- ccf_test[ ,11]

## stratified folds for cross-validation:
foldId <- createFolds(Y_tr, k = 10, list = TRUE, returnTrain = TRUE)
lapply(foldId, function(ii) table(Y_tr[ii]))
```

# rpart using "smote" resampling with 10 selected features
```{r}
set.seed(10)
rpart_s_sf <- train(Class ~., data = ccf_train, method = "rpart", parms = list(split = "information"), metric = "ROC", trControl=ctr_s, tuneLength = 30)
```

```{r}
rpart_s_sf

# test set results using confusion matrix
pred_rpart_s_sf <- predict(rpart_s_sf, ccf_test)
confusionMatrix(pred_rpart_s_sf, Y_ts)

# Predicting Class probabilities
prob_rpart_s_sf <- predict(rpart_s_sf, ccf_test, type = "prob")
head(prob_rpart_s_sf)

# AUC using pROC package
ROC_rpart_s_sf <- roc(Y_ts, prob_rpart_s_sf [ ,"Fraud"])
plot(ROC_rpart_s_sf, print.thres = c(0.0001,0.001, 0.01, 0.1, 0.5, 0.9, 0.999), col ="red")
ROC_rpart_s_sf

# AUC using ROCR package
pr_rpart_s_sf <- prediction(prob_rpart_s_sf[ , 1], Y_test)
prf_rpart_s_sf <- performance(pr_rpart_s_sf, measure = "tpr", x.measure = "fpr")
plot(prf_rpart_s_sf, col = "red" )
abline(0,1)
auc_s_sf <- performance(pr_rpart_s_sf, measure = "auc")
auc_s_sf <- auc_s_sf@y.values[[1]]
auc_s_sf
```


